Some usefull words/expressions/sentences

### 2018-07-28 phrases.Rmd
table 1

@@

>>>>

-  jargon ['dʒɑ:ɡən, -ɡɔn]

```
======== 辞典翻译: jargon ========
  n. 行话，术语；黄锆石
============ 网络释义 ============
----------- jargon -----------
  行话
  专门术语
  术语
------ phonemic jargon -------
  音韵性乱语
------ Computer Jargon -------
  电脑流行语
  行话
```

@@

## lumley2011complex - Complex surveys: a guide to analysis using R

- In everyday speech, "taking a random sample" of 1000 individuals means a sampling procedure when any subset of 1000 people from the population is equally likely to be selected.

- The expected value of the estimate is the value of the estimate when we select person $i$, times the probability of selecting person $i$, added up over all peole in the population.

- Sampling weights: A sampling weight of 1000 means that the observation represents 1000 individuals in the population.
